rough outline

### 2022-04-27 outline.Rmd
Joined deaths_df and world_pop so we can make more graphs

>>>>

#Join the data sets so we can overlay the two graph or do a stacked barchart?

- `full_join(x, y, by = )`:return all rows and all columns from both x and y. Where there are not matching values, returns NA for the one missing.
- full join deaths_df and world_pop2

```{r}
joined_df <- full_join(deaths_df, world_pop2, by = c("country" = "Country.Name"))
glimpse(joined_df)

```
```{r}
ggplot(joined_df, aes(fill=Count, y=country, x=year)) + 
  geom_bar(position="stack", stat="identity")
